What's hot and what's not:\\Windowing developer topic analysis

### 2009-04-09 lda-paper.tex
Some edits and some more maxdb75 stuff Need more maxdb75 stuff

>>>>

%XXX Edit
% Was reading lda.report
Bug tracker URLs were common during some months. For instance in the
last month of MaxDB 7.500 development every topic contained 1 unique
Bug tracker URL, this pattern did not occur in the previou month. We
investigated the actual revisions and we did find there was difference
in behaviour between and that the last month of development commits
were mostly referencing the bug tracker. If the topics of one month
were 20 or more unique bug tickets being addressed, the global LDA
analysis would probably miss this, yet these bug tickets were the
focus of development for that month and not necessarily globally
relevant.
